Descriptive_Stats

### 2023-10-11 Code/RankComparison.Rmd
Fixed name of file

This is seeing what would happen if we remove prelims, the sample sizes in the
test become very small: 26 observations and 9 clusters.
```{r}
nations_noprelim <- read.csv("../Data/Clusrank2019vs2022PrelimsOnly.csv")
colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

@@

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds", 
                exact = TRUE, B = 1000000)
```

>>>>

This is seeing what would happen if we remove prelims, the sample sizes in the
test become very small: 26 observations and 9 clusters.
```{r}
nations_noprelim <- read.csv("../Data/Clusrank2019vs2022NoPrelims.csv")
colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

@@

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_data,
                method = "ds", 
                exact = TRUE, B = 1000000)
```
```{r}
new_2023 <- read.csv("../Data/ClusrankNatVsWorld2023.csv")
colnames(new_2023) <- c("Time", 'Athlete', "Year")
```

```{r}
set.seed(1)
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_2023,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_2023,
                method = "ds",
                exact = TRUE, B = 1000000)
```
